The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-03-30 methods/ms.tex
ms.tex - removed middle flagger figure
example_waterfalls - times flagged

\Figure{flagger_withglitch}{An illustration of the flagging process
using the waterfall plot. The glitch apparent at middle right is the
same one whose time series is shown in Figure
\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect
of the glitch also propagates over the other bolometers, appearing as
a horizontal stripe.}  {fig:Flag1}{1.0}

\Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
removed from subsequent analysis.}{fig:Flag2}{1.0}

\Figure{flagger_glitchgone}{A rescaled version of the data with the
bad data removed.  The effect of the glitch on the other bolometers is
now more apparent; this too is flagged out in subsequent
analysis.}{fig:Flag3}{1.0}

>>>>

\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of the
flagging process using the waterfall plot. Left: The glitch apparent at middle
right is the same one whose time series is shown in Figure
\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect of the
glitch also propagates over the other bolometers, appearing as a horizontal
stripe. Right: The same data displayed with the time point including the glitch
flagged out and rescaled}  {fig:Flag1}{1.0}

%this figure failed to create automatically and wasn't really that useful
%anyway
% \Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
% removed from subsequent analysis.}{fig:Flag2}{1.0}

% \Figure{flagger_glitchgone}{A rescaled version of the data with the
% bad data removed.  The effect of the glitch on the other bolometers is
% now more apparent; this too is flagged out in subsequent
% analysis.}{fig:Flag3}{1.0}
